Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-27 latex/comp_or.tex
Tests with parallel pallets were not good
Shims_p is better with 1 process

@@

		\multirow{6}{*}{$1.2$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$                & 5.70  & 3.09  & 2.94  & 2.90  & 2.79  & 5.70  & 0.91  \\%2312
		                       &                                 & {\bf run-time (s)} & 1     & 3     & 7     & 26    & 97    & 267   & 70  \\%390
		                       \cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$                & 6.42  & 3.78  &  3.19 & 3.17  & 2.97  & 5.87  & 1.00  \\ %2540
                               &                                 & {\bf run-time (s)} & 16    & 282   &  314  & 1334  & 6945  & 18883 & 1  \\ %27162
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\                               
		\midrule
		\multirow{6}{*}{$1.5$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$                & 8.15  & 4.22  & 4.40  & 4.01  & 3.51  & 7.08  &   \\
		                       &                                 & {\bf run-time (s)} & 1     & 5     & 12    & 45    & 244   & 737   &   \\
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$                & 9.50  & 5.01  & 4.60  & 4.28  &&&\\
		                       &                                 & {\bf run-time (s)} & 9     & 344   & 787   & 1525  &&&\\
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\		                       
		\midrule
		\multirow{6}{*}{$2.0$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$                & 11.31 & 6.29  & 5.54  & 5.83  & 5.05  & 10.63 &   \\
		                       &                                 & {\bf run-time (s)} & 2     & 14    & 34    & 106   & 477   & 2417  &   \\
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$                &&&&&&&\\
		                       &                                 & {\bf run-time (s)} &&&&&&&\\
		\cmidrule{2-10}		                       
		                       &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\
		\bottomrule

>>>>

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpACO computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}

	\end{center}
	\caption{ Scenario 1 performances with $1.5 \times volume$. }
	\label{fig:scenario1data50}
\end{figure}

@@

		\multirow{8}{*}{$1.2$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               &   &   &   &   &   &   &   \\%
                               &                                 & {\bf run-time (s)} &      &      &      &     &     &    &   \\%\cmidrule{2-10}

		                       &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               & 5.70  & 3.09  & 2.94  & 2.90  & 2.79  & 5.70  & 0.91  \\%2312
		                       &                                 & {\bf run-time (s)} & 1     & 3     & 7     & 26    & 97    & 267   & 70  \\%390
		                       \cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$               & 6.42  & 3.78  &  3.19 & 3.17  & 2.97  & 5.87  & 1.00  \\ %2540
                               &                                 & {\bf run-time (s)} & 16    & 282   &  314  & 1334  & 6945  & 18883 & 1  \\ %27162
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$               &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\                               
		\midrule
		\multirow{6}{*}{$1.5$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               & 8.15  & 4.22  & 4.40  & 4.01  & 3.51  & 7.08  & 0.91  \\%3137
		                       &                                 & {\bf run-time (s)} & 1     & 5     & 12    & 45    & 244   & 737   & 30  \\%1026
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$               & 9.50  & 5.01  & 4.60  & 4.28  & 3.78  & 7.15  & 1.00 \\ %3432

		                       &                                 & {\bf run-time (s)} & 9     & 344   & 787   & 1525  & 7525  & 21443 & 1 \\%30493
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$               &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\		                       
		\midrule
		\multirow{6}{*}{$2.0$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               & 11.31 & 6.29  & 5.54  & 5.83  & 5.05  & 10.63 & 0.94  \\%4465
		                       &                                 & {\bf run-time (s)} & 2     & 14    & 34    & 106   & 477   & 2417  & 10  \\%3000
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$               & 12.70 & 7.09  & 5.97  & 5.91  & 5.31  & 10.69 & 1.00  \\%4767
		                       &                                 & {\bf run-time (s)} & 5     & 189   & 784   & 1456  & 7758  & 20330 & 1  \\%29544
		\cmidrule{2-10}		                       
		                       &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\
		\bottomrule
